A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex

Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently, it has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.  This suggest that its worker population that should represent a diverse set of languages.

A demographic study by \newcite{ipeirotis:2010:demographics} focused on age, gender, martial status, income levels, motivation for working on MTurk, and whether workers used it as a primary or supplemental form of income.  The study contrasted Indian and US workers. 
A number of other studies have informally investigated Turkers' language abilities.  \newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu).  \newcite{irvine:10} had Turkers evaluate the accuracy of translations that had been automatically inducted from monolingual texts.  They examined translations of 100 words in 42 low-resource languages, reported geolocated countries for their workers (India, the US, Romania, Pakistan, Macedonia, Latvia, Bangladesh and the Philippines).  Irvine and Klementiev discussed the difficulty of quality control and assessing the plausibility of workers' language skills for rare languages, which we address in this paper.

@@

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &129,049\\
How many years have you spoken [HIT language]?&159,807\\
How many years have you spoken English?&159,808\\
What country do you live in?&329,033\\
Current location (collected automatically)& 329,033\\
\hline\\
Total assignments& 329,033\\
Total unique workers& 6,034\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently, it has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries \cite{AmazonRequesterTour}.  This suggests that its worker population should represent a diverse set of languages.

A demographic study by \newcite{ipeirotis:2010:demographics} focused on age, gender, martial status, income levels, motivation for working on MTurk, and whether workers used it as a primary or supplemental form of income.  The study contrasted Indian and US workers. \newcite{Ross2010} completed a longitudinal follow-on study. 
A number of other studies have informally investigated Turkers' language abilities.  \newcite{munro-tily:2011} compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu).  \newcite{irvine:10} had Turkers evaluate the accuracy of translations that had been automatically inducted from monolingual texts.  They examined translations of 100 words in 42 low-resource languages, reported geolocated countries for their workers (India, the US, Romania, Pakistan, Macedonia, Latvia, Bangladesh and the Philippines).  Irvine and Klementiev discussed the difficulty of quality control and assessing the plausibility of workers' language skills for rare languages, which we address in this paper.

@@

%%%%%%%%%%%%%%% SURVEY TABLE %%%%%%%%%%%
\begin{table*}[h]
\centering
\begin{tabular}{lc}\hline\hline\\
Is [HIT language/English] your native language? &NUM\\
How many years have you spoken [HIT language]?&NUM\\
How many years have you spoken English?&NUM\\
What country do you live in?&308,079\\
Current location (collected automatically)& 308,079\\
\hline\\
Total assignments& 308,079\\
Total unique workers& 5,271\\
\hline\hline
\end{tabular}
\caption{Demographic survey questions and number of assignments with valid responses for each}
\label{survey-tab}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
